Fluoroproj: Title to be decided later

### 2023-07-07 manuscript/manuscript.qmd
more local changes

```{r read_tabl1, echo=FALSE, message=FALSE}
table1 <- read_csv(here::here("data/cleaned_phycotech_cyano_data.csv")) 
```

>>>>

```{r read_tabl1, echo=FALSE, message=FALSE}
table1 <- read_csv(here::here("data/cleaned_phycotech_cyano_data.csv")) %>%
  select(-family) %>%
  mutate(biovolume = round(biovolume, 1),
         relative_biovolume = round(relative_biovolume, 5))
```
